Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-10-31 eqm_profiles.tex
turn lemma 3 strategy profile part into prose

In period $t$, the patron invests $R_{pt} = \max\left\{\frac{\beta}{1-\de} - \left( Q_{s,t-1} - \mu - L_{s,t-1}\right),0\right\}$ to augment the status quo payoffs of the secessionists, $q_{st}$. Player $c$ then chooses $R_{ct} =0$ so that playing status quo is a best response for both inside players. (SQ,SQ) is played in the third stage and the game continues to period $t+1$.

If instead $R_{pt} < \frac{\beta}{1-\de} - \left( Q_{s,t-1} - \mu - L_{s,t-1}\right)$ (i.e. assumption 3 doesn't hold), player $c$ will invest $R_{ct} = l_{st} - \left(q_{st} + R_{pt} \right) + \ve$, for $\ve$ small, to augment $l_{st}$. In this case, status quo remains a best response for the government but cede becomes the best response for the secessionists. The game ends with the secessionist territory being reunited.

\begin{enumerate}	
	\item Patron would like $L_{gt} > Q_{gt}$ to achieve recognition directly. Must invest to augment $l_{gt}$
		\begin{itemize}
			\item Equivalent to $l_{gt} + R_{pt} > q_{gt} + R_{ct}$ / $L_{g,t-1} + R_{pt} > Q_{g,t-1} + R_{ct}$ / $R_{pt} > R_{ct} + \left( Q_{g,t-1} - L_{g,t-1}\right)$
				\begin{itemize}
					\item $R_{ct} \leq \frac{\nu}{1-\de} \Rightarrow$ $R_{pt} > \frac{\nu}{1-\de} + \left( Q_{g,t-1} - L_{g,t-1}\right)$ allows the patron to ensure the original inequality
					\item Since patron is willing to pay up to $R_{pt} = \frac{\lambda +\mu + \beta}{1-\de} - \mu$, when $\frac{\lambda +\mu + \beta}{1-\de} -\mu \leq \frac{\nu}{1-\de}$, patron will invest 0 in $l_{gt}$. $R_{ct} = 0$ as well.
					\item If instead assumption 4 did not hold and $R_{pt} > \frac{\nu}{1-\de} + \left( Q_{g,t-1} - L_{g,t-1}\right)$, patron will invest this amount to augment $l_{gt}$. Again, $R_{ct} = 0$. (Cede, SQ) is played and game ends.
				\end{itemize}
		\end{itemize}
	\item Patron might want to instigate fighting to have a $p_{1s}$ probability of achieving recognition indirectly. If $\frac{\lambda p_{1s} - \alpha (1-p_{1s}) + \mu + \beta}{1 - \de} -\mu$ is positive, invest in $w_{st}$ to change $\omega_{st}$. Will not invest when the quantity is non-positive. Inequality is $\omega_{st} > Q_{st}$
		\begin{itemize}
			\item $\omega_{st} = -\zeta_{s}(1-\de) + W_{st}p_{1s} + L_{st}(1-p_{1s}) > Q_{st}$
			\item $-\zeta_{s}(1-\de) + (W_{s,t-1}+R_{pt})p_{1s} + L_{s,t-1}(1-p_{1s}) > Q_{s,t-1} - \mu + R_{ct}$
			\item $R_{pt}p_{1s} > R_{ct} - \mu + Q_{s,t-1} - \left(-\zeta_{s}(1-\de) + W_{s,t-1}p_{1s} + L_{s,t-1}(1-p_{1s})\right)$
			\item $R_{ct} \leq \frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de}$, so if $R_{pt}p_{1s} > \frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de} - \mu + Q_{s,t-1} - \left(-\zeta_{s}(1-\de) + W_{s,t-1}p_{1s} + L_{s,t-1}(1-p_{1s})\right)$, $R_{ct}=0$ and (SQ,Fight) is played in third stage. Outcome depends on war lottery.
			\item Patron will spend at most $\frac{\lambda p_{1s} - \alpha (1-p_{1s}) +\mu + \beta}{1 -\de} - \mu$
				\begin{itemize}
					\item So need
						\begin{multline}
							\textstyle p_{1s}\left[\frac{\lambda p_{1s} - \alpha (1-p_{1s}) +\mu + \beta}{1 -\de} - \mu\right] < \frac{\lambda p_{1s} - \alpha (1-p_{1s}) +\mu + \beta}{1 -\de} - \mu \leq \frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de} - \mu \\ \leq \frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de} - \mu + Q_{s,t-1} - \left(-\zeta_{s}(1-\de) + W_{s,t-1}p_{1s} + L_{s,t-1}(1-p_{1s})\right)
						\end{multline}
				\end{itemize}
		\end{itemize}
	\item Patron could also invest in $q_g$ to counter investment by $c$ in government's payoffs. But this would only been needed if $c$ had incentive to invest in $g$ playing Fight, and we've ruled that out.
\end{enumerate}

>>>>

On the equilibrium path, the patron invests to avoid the reunification outcome. That is, it invests in the secessionists' status quo payoffs to deter the international community from investing in the secessionists' payoffs from ceding. In period $t$, the patron invests $R_{pt} = \max\left\{\frac{\beta}{1-\de} - \left( Q_{s,t-1} - \mu - L_{s,t-1}\right),0\right\}$ to augment the status quo payoffs of the secessionists, $q_{st}$. Player $c$ then chooses $R_{ct} =0$ so that playing status quo is a best response for both inside players. (SQ,SQ) is played in the third stage and the game continues to period $t+1$.

If instead $R_{pt} < \frac{\beta}{1-\de} - \left( Q_{s,t-1} - \mu - L_{s,t-1}\right)$ (i.e. assumption 3 doesn't hold), player $c$ will invest $R_{ct} = l_{st} - \left(q_{st} + R_{pt} \right) + \ve$, for $\ve$ small, to augment $l_{st}$. In this case, status quo remains a best response for the government but cede becomes the best response for the secessionists. The game ends with the secessionist territory being reunited. This path is ruled out by Assumption 3 (see Lemma 2).

The patron would prefer to invest to provoke the recognition outcome, which it can attempt to do directly by investing in the government's payoffs from ceding, $l_{gt}$. If the patron invests $R_{pt} > \frac{\nu}{1-\de} + \left( Q_{g,t-1} - L_{g,t-1}\right)$ to augment $l_{gt}$, player $c$ will then choose $R_{ct} = 0$ and cede will be the best response for the government. Status quo remains the best response for the secessionists, so the game ends with the secessionists gaining recognition. This path is ruled out by Assumption 4 (see Lemma 3).

As long as $R_{pt} \leq \frac{\nu}{1-\de} + \left( Q_{g,t-1} - L_{g,t-1}\right)$, player $c$ will counter with $R_{ct} = R_{pt} - \left( Q_{g,t-1} - L_{g,t-1}\right)$ to augment $l_{gt}$. This makes status quo a best response for the government as well as for the secessionists so that the status quo equilibrium is played and the game continues to period $t+1$. Note that the optimal investments in the government's payoffs zero.

\begin{enumerate}		
	\item Patron might want to instigate fighting to have a $p_{1s}$ probability of achieving recognition indirectly. If $\frac{\lambda p_{1s} - \alpha (1-p_{1s}) + \mu + \beta}{1 - \de} -\mu$ is positive, invest in $w_{st}$ to change $\omega_{st}$. Will not invest when the quantity is non-positive. Inequality is $\omega_{st} > Q_{st}$
		\begin{itemize}
			\item $\omega_{st} = -\zeta_{s}(1-\de) + W_{st}p_{1s} + L_{st}(1-p_{1s}) > Q_{st}$
			\item $-\zeta_{s}(1-\de) + (W_{s,t-1}+R_{pt})p_{1s} + L_{s,t-1}(1-p_{1s}) > Q_{s,t-1} - \mu + R_{ct}$
			\item $R_{pt}p_{1s} > R_{ct} - \mu + Q_{s,t-1} - \left(-\zeta_{s}(1-\de) + W_{s,t-1}p_{1s} + L_{s,t-1}(1-p_{1s})\right)$
			\item $R_{ct} \leq \frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de}$, so if $R_{pt}p_{1s} > \frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de} - \mu + Q_{s,t-1} - \left(-\zeta_{s}(1-\de) + W_{s,t-1}p_{1s} + L_{s,t-1}(1-p_{1s})\right)$, $R_{ct}=0$ and (SQ,Fight) is played in third stage. Outcome depends on war lottery.
			\item Patron will spend at most $\frac{\lambda p_{1s} - \alpha (1-p_{1s}) +\mu + \beta}{1 -\de} - \mu$
				\begin{itemize}
					\item So need
						\begin{multline}
							\textstyle p_{1s}\left[\frac{\lambda p_{1s} - \alpha (1-p_{1s}) +\mu + \beta}{1 -\de} - \mu\right] < \frac{\lambda p_{1s} - \alpha (1-p_{1s}) +\mu + \beta}{1 -\de} - \mu \leq \frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de} - \mu \\ \leq \frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de} - \mu + Q_{s,t-1} - \left(-\zeta_{s}(1-\de) + W_{s,t-1}p_{1s} + L_{s,t-1}(1-p_{1s})\right)
						\end{multline}
				\end{itemize}
		\end{itemize}
	\item Patron could also invest in $q_g$ to counter investment by $c$ in government's payoffs. But this would only been needed if $c$ had incentive to invest in $g$ playing Fight, and we've ruled that out.
\end{enumerate}
